Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-12-13 Manuscript/Imputation_of_Incomplete_Multilevel_Data.tex
Update pdf

\author{
Hanne I. Oberman\\Utrecht University \And Johanna Munoz Avila\\Julius
Center for Health Sciences and Primary Care,\\
University Medical Center Utrecht, Utrecht University,\\
Utrecht, The Netherlands \AND Thomas P. A. Debray\\Julius Center
for Health Sciences and Primary Care \And Gerko Vink\\Utrecht University
\AND Valentijn M. T. de Jong\\Julius Center for Health Sciences and
Primary Care,\\
University Medical Center Utrecht, Utrecht University,\\
Utrecht, The Netherlands
}
\title{Imputation of Incomplete Multilevel Data with \pkg{mice}}

\Plainauthor{Hanne I. Oberman, Johanna Munoz Avila, Thomas P. A.
Debray, Gerko Vink, Valentijn M. T. de Jong}
\Plaintitle{Imputation of Incomplete Multilevel Data with mice}
\Shorttitle{Multilevel \pkg{mice}}

@@

Impute the data:

@@

\begin{itemize}
\item
  Adding evaluations of the imputations such as convergence checks
\item
  Adding some kind of help function to mice that suggests a suitable
  predictor matrix to the user, given a certain analysis model.
\item
  Adding a \texttt{multilevel\_ampute()} wrapper function in mice.
\item
  Exporting \texttt{mids} objects to other packages like \texttt{lme4}
  or \texttt{coxme}?
\item
  Adding a ICC=0 dataset to show that even if there is no clustering it
  doesn't hurt.
\item
  Show use case for deductive imputation for cluster level variables?
\item
  env dump in repo
\end{itemize}

>>>>

\author{
Hanne I. Oberman\\Utrecht University \And Johanna Munoz\\Julius Center
for Health Sciences and Primary Care,\\
University Medical Center Utrecht, Utrecht University,\\
Utrecht, The Netherlands \AND Thomas P. A. Debray\\Julius Center
for Health Sciences and Primary Care \And Gerko Vink\\Utrecht University
\AND Valentijn M. T. de Jong\\Julius Center for Health Sciences and
Primary Care,\\
University Medical Center Utrecht, Utrecht University,\\
Utrecht, The Netherlands
}
\title{Imputation of Incomplete Multilevel Data with \pkg{mice}}

\Plainauthor{Hanne I. Oberman, Johanna Munoz, Thomas P. A. Debray, Gerko
Vink, Valentijn M. T. de Jong}
\Plaintitle{Imputation of Incomplete Multilevel Data with mice}
\Shorttitle{Multilevel \pkg{mice}}

@@

@@

\begin{itemize}
\item
  Adding evaluations of the imputations such as convergence checks
\item
  Adding some kind of help function to mice that suggests a suitable
  predictor matrix to the user, given a certain analysis model.
\item
  Adding a \texttt{multilevel\_ampute()} wrapper function in mice.
\item
  Exporting \texttt{mids} objects to other packages like \texttt{lme4}
  or \texttt{coxme}?
\item
  Adding a ICC=0 dataset to show that even if there is no clustering it
  doesn't hurt.
\item
  Show use case for deductive imputation for cluster level variables?
\item
  env dump in repo
\item
  I don't know if in your article you cover something about model
  complexity, for example sometimes I have to switch from 2l. methods to
  1l. methods just because the model didn't converge.. this is due to
  the considered imputation model is very complex regarding the amount
  of information counted\ldots{} I know that a solution for an
  imputation model with many predictors is to check correlation plots as
  you did or use quickpred().. (maybe you can add this somewhere after
  the correlation plots)\ldots..But as for cluster specification, I
  don't know if besides plots of distribution per cluster there is
  something else can be done to see if i have to use 1l. or 2l. for a
  given variable, also I have no idea.. how to test which is better
  between 2l.norm or 2l.2stage.norm.
\end{itemize}
